Compare pseqs

### 2019-05-17 comparepseqs.Rmd
Perm 1000

 ```{r adonis calculation}
if (!file.exists("rds-comparepseqs/beta.diversity.rds")) {
    covariates.min <- c("BL_AGE", "SEX")
    covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                         "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                         "BL_USE_RX_C08", "BL_USE_RX_C09")

    betadiversity <- mclapply(c2l(names(pseq)), function(x)
        list(min = calculateadonis(dset = meta(pseq[[x]]),
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1),
             full = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1)),
        mc.cores = length(pseq))

@@

str(betadiversity)

>>>>

 ```{r adonis calculation}
if (!file.exists("rds-comparepseqs/beta.diversity.rds")) {

    covariates.min <- c("BL_AGE", "SEX")
    covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                         "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                         "BL_USE_RX_C08", "BL_USE_RX_C09")

    betadiversity <- mclapply(c2l(names(pseq)), function(x)
        list(min = calculateadonis(dset = meta(pseq[[x]]),
                                   matrix = bray.dist.matrix[[x]],
                                   covariates = covariates.min,
                                   npermutations = 1000),
             full = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.full,
                                    npermutations = 1000)),
        mc.cores = length(pseq))

@@
